Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-23 paper/ms.tex
manuscript update and it's 17:30

\subsubsection{CHIRON}
9 spectra with CTIO1.5/CHIRON, from January 28 through March 14, 2020.
6 were usable.

\subsubsection{FEROS}
N spectra with XXX/FEROS

\subsubsection{Veloce}
M spectra with AAT/Veloce.

@@

\newpage
\subsubsection{Color Photometry}

@@

\clearpage
\input{model_comparison_table.tex}
\input{model_posterior_table.tex}
\clearpage

>>>>

Reconaissance spectroscopic follow-up is an essential step in vetting
planet candidates.  Medium to high-resolution spectra enable physical
characterization of the star and therefore planet.  Reducing multiple
spectra to a radial velocity time-series can enable planet mass
measurements, and also set limits on the mass of any nearby
companions.  Finally, if there are close or bright companions,
reconaissance spectra can also reveal the presence of a secondary set
of stellar lines.

\subsubsection{CHIRON}
We acquired nine spectra with CTIO1.5/CHIRON, from January 28 2020 through
March 14 2020.
Six met our signal-to-noise requirements for radial velocity
measurements.

{\bf George TODO: please describe the formal secondary line search in
more depth in this paragraph}
We searched for secondary lines in the CHIRON spectra by
cross-correlating against a {\bf template of some kind}.
This rules out lines with flux ratios of $\approx 2\%$, if the
lines are well-separated in velocity.
We measured the radial velocities against the same template.
To derved the star's physical parameters, we cross-correlated the
template against {\bf something}, and used the {\bf
\texttt{nameofcode}}. 
This yielded:
\begin{align}
  T_{\rm eff}   &= 5946 \pm 39\,{\rm K}, \nonumber \\
  \log g        &= 4.48 \pm 0.03, \nonumber \\
  {\rm [Fe/H] } &= -0.065 \pm 0.035, \nonumber \\
  v \sin i      &= 17.48 \pm 0.15\,{\rm km\,s}^{-1}.
\end{align}
These spectroscopic parameters were used in our final analysis 
of the system (Section~\ref{sec:system}).

\subsubsection{FEROS}
We acquired N spectra with XXX/FEROS.

\subsubsection{Veloce}
We acquired M spectra with AAT/Veloce.

@@

\subsubsection{Color Photometry}

@@

\clearpage
\input{TOI837_phot_table.tex}
\input{TOI837_rv_table.tex}
\input{model_comparison_table.tex}
\input{model_posterior_table.tex}
\clearpage
